Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-22 paper.tex
minor corrections
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Finally, ML techniques are already being used in the software verification area \cite{mlswverif,nguyen}. For instance, Hamel \cite{mlswverif} proposes to induce a theory, through ML, that fits a test set for a program, in such a way that it implement the respective test set. ML is already being employ in space state reduction, ML technique can be used also for invariant generation

>>>>

Finally, ML techniques are already being used in the software verification area \cite{mlswverif,nguyen}. For instance, Hamel \cite{mlswverif} proposes to induce a theory, through ML, that fits a test set for a program, in such a way that it implements the respective test set. ML is already being employed in space state reduction, ML technique can be used also for invariant generation.
